---
title: Home
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)
library(DT)
# library(widgetframe)

ties_data <- tibble::tribble(~name,      ~number_of_ties, ~no_steps,  ~fold_in_half, ~end_tied_with, ~url,                                           ~shaping_difficulty,  ~no_loop_thrus,
                             "rosebud1",   1,              7,         "Y",           "little",       "https://www.youtube.com/watch?v=s-S1WSFTpuU",   1,                   0,
                             "rosebud2",   1,              5,         "N",       "little",       "https://www.youtube.com/watch?v=-diYX2FH_AE",   1,                   0,
                             "vidalia",    1,              0,        "N",       "little", "https://www.youtube.com/watch?v=ENYCWzrB9d8",   1,                   2,
                             "valentine",  1,              0,        "Y",       "little", "https://www.youtube.com/watch?v=XwvNQYIZnSI",   3,                   0,
                             "sweetheart", 1,              0,        "Y",       "little", "https://www.youtube.com/watch?v=nfoqEexLghI",   4,                   2,
                             "romance",    1,              0,        "Y",       "little", "https://www.youtube.com/watch?v=XdRsQ3KuTqM",   1,                   0,
                             "cupid",      1,              0,        "N",        "both", "https://www.youtube.com/watch?v=VWfEccMG_HI",   5,                   1,
                             "vampire",    1,              0,        "Y",        "little", "https://www.youtube.com/watch?v=wFTkThHwagI",   1,                   0,
                             "embrace",    1,              0,        "Y",        "little", "https://www.youtube.com/watch?v=mwfLpoyqeKE",   1,                   2)  %>% 
  mutate(image = paste0('<img src = "/img/', name, '.jpg"></img>'),
         name = paste0("<a href='", url, "'target='_blank'>", name, "</a>")
         ) %>% 
  select(-url)

```


# Ben Gin's Blog
This is a blog of things that I like to do.

Currently only has Ties, but I intend to add pallet furniture and other craft projects.

## Tie Summary
I stumbled across a video on youtube showing two different ways of tying tie knots, and that led me to the discovery that there are 100+ ways to tie a tie.

Below is a summary table of the tie knots that I have tried. I intend to come up with a calculation of difficulty using the columns in this table as inputs.

```{r, echo=FALSE}
ties_data %>% 
  datatable(escape = FALSE, options = list(pageLength = 5, autowidth = TRUE), rownames = FALSE)

# widgetframe::frameWidget(ties_summ_tbl)
```


## Posts
