---
title: Home
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)
library(DT)
# library(widgetframe)

ties_data <- tibble::tribble(~name,              ~no_ties, ~no_steps,  ~fold_in_half, ~end_tied_with, ~url,                                              ~shaping_difficulty,       ~no_loop_thrus,
                             "rosebud1",         1,        6,          "Y",           "little",       "https://www.youtube.com/watch?v=s-S1WSFTpuU",     1,                         1,
                             "rosebud2",         1,        4,          "N",           "little",       "https://www.youtube.com/watch?v=-diYX2FH_AE",     2,                         0,
                             "vidalia",          1,        5,          "N",           "little", "https://www.youtube.com/watch?v=ENYCWzrB9d8",     2,                         3,
                             "valentine",        1,        5,          "Y",           "little", "https://www.youtube.com/watch?v=XwvNQYIZnSI",     3,                         1,
                             "sweetheart",       1,        4,          "Y",           "little", "https://www.youtube.com/watch?v=nfoqEexLghI",     4,                         3,
                             "romance",          1,        5,          "Y",           "little", "https://www.youtube.com/watch?v=XdRsQ3KuTqM",     3,                         5,
                             "cupid",            1,        3,          "N",           "both", "https://www.youtube.com/watch?v=VWfEccMG_HI",     5,                         1,
                             "vampire",          1,        5,          "Y",           "little", "https://www.youtube.com/watch?v=wFTkThHwagI",     1,                         0,
                             "embrace",          1,        3,          "Y",           "little", "https://www.youtube.com/watch?v=mwfLpoyqeKE",     1,                         3,
                             "deivao_twist",     1,        6,          "N",           "little", "https://www.youtube.com/watch?v=mCANkZKtES4",     1,                         3,
                             "trinity",          1,        4,          "N",           "little", "https://www.youtube.com/watch?v=IX_GixAhXeY",     2,                         2,
                             "trinity_eldredge", 1,        5,          "N",           "little", "https://www.youtube.com/watch?v=Ls_MgWrTVrk",     1,                         2)  %>% 
  mutate(image = paste0('<img src = "/img/', name, '.jpg"></img>'),
         name = paste0("<a href='", url, "'target='_blank'>", name, "</a>")
         ) %>% 
  select(-url)

```


# Ben Gin's Blog
This is a blog of things that I like to do/make including:

* Learning new tie knots
* Building pallet furniture
* Making craft projects

## Tie Summary
I stumbled across a video on youtube showing two different ways of tying tie knots, and that led me to the discovery that there are 100+ ways to tie a tie.

Below is a summary table of the tie knots that I have tried. I intend to come up with a calculation of difficulty using the columns in this table as inputs.

Table updated: 2020-05-15

```{r, echo=FALSE}
ties_data %>% 
  datatable(escape = FALSE, options = list(pageLength = 5, autowidth = TRUE), rownames = FALSE,
            colnames = c('Name', 'No. ties', 'No. steps', 'Fold in half', 'End', 'Shaping difficulty', 'No. loop thrus', 'image'))

# widgetframe::frameWidget(ties_summ_tbl)
```

## Pallet Furniture
In 2011 I helped a colleague make a mobile pallet kitchen table, and so found out that I could obtain pallets from my work palce. Since then, I have obtained pallets from wherever I could find them. I disassemble them and store the wood ready for any projects. 

## Craft Projects
I also like to try my hand at any other craft projects.

## Posts
