---
title: "Home"
output:
    blogdown::html_page:
      css: "/css/my_style.css"
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)
library(DT)

source("tie_functions.R")
source("tie_config.R")

```




# Ben Gin's Blog
This is a blog of things that I like to do/make including:

* Learning new tie knots
* Building pallet furniture
* Making craft projects

Most of the pallet and craft posts will be retrospective, as they are completed projects from past years.

## Pallet Furniture
In 2011 I helped a colleague make a mobile pallet kitchen table, and so found out that I could obtain pallets from my work place. Since then, I have obtained pallets from wherever I could find them (but no longer from work). I disassemble them and store the wood ready for any projects. To disassemble pallets, I use the [no tools method](https://www.youtube.com/watch?v=cLwKUeez1OE) first. If the configuration of the wood does not allow for this technique, I then resort to a crow bar and rubber mallet.

## Craft Projects
I also like to try my hand at any other craft projects.

## Tie Summary
I stumbled across a video on youtube showing two different ways of tying tie knots, and that led me to the discovery that there are 100+ ways to tie a tie. Starting from a work initiative to "suit up Tuesday" (March 2020), I decided to make it mean "Tie Tuesday", and so have been doing one new tie knot a week.

Below is a summary table of the tie knots that I have tried. The "Name" column contains a hyperlink to the youtube video for that knot, and the "Image" column contains the image which can be enlarged by clicking (or tapping) on the image. The "Difficulty" column is a calculated value (details of the calculation can be found in this [post](/post/tie-difficulty-calculation)) and the numbers are relative with a maximum of 10 for what I consider the most difficult tie knot.

A more detailed table that is arrangeable and searchable can be found in this [post](/post/tie-detailed-table/).

Table updated: `r tbl_update_date`

```{r, echo=FALSE}
ties_data %>%
  mutate(overall_difficulty = as.character(overall_difficulty)) %>% 
  datatable(escape = FALSE, 
            options = list(dom = 't', 
                           ordering = FALSE, 
                           autowidth = TRUE, 
                           pageLength = nrow(ties_data), 
                           columnDefs = list(list(width='33%', targets = list(0,1)),
                                             list(width='25%', targets = list(2)),
                                             list(className = 'dt-center', targets = list(0,1)))),
            rownames = FALSE, 
            colnames = c('Name', 'Difficulty', 'Image')
            )

```



## Posts
